Rubin Observatory Pointing Algorithm and Survey Simulation

### 2025-02-05 ms.tex
text

\title{Rubin Observatory Pointing Algorithm and Simulations}

@@

\subsection{ToO Events}
Describe the default ToO events we inject by default. xxx-was there a citeable thing that came out of the workshop?

@@

Rather than use a fixed set of specific pointings, we adopt a full-sky tesselation and then randomize the orientation of that tesselation nightly. So on any given night, there are XXX potential coordinates the telescope could be pointed to, but those positions will not be reused on subsequent nights.

@@

We can combine the above two techniques. In order to force observations on certain time scales, we can use the MDP to observe an area of the sky, and once those observations are completed, spawn new scheduled observations on the same area to be completed later.

@@

There are a number of potential Target of Opportunity

>>>>

\title{Rubin Observatory Pointing Algorithm and Survey Simulation}

@@

\subsection{ToO Events}

Describe the default ToO events we inject by default. Report from the ToO workshop \citep{Andreoni2022}

@@

Rather than use a fixed set of specific pointings, we adopt a full-sky tesselation and then randomize the orientation of that tesselation nightly as done in \citet{Rothchild2019}. So on any given night, there are XXX potential coordinates the telescope could be pointed to, but those positions will not be reused on subsequent nights.

@@

We can combine the above two techniques. In order to force observations on certain time scales, we can use the MDP to observe an area of the sky, and once those observations are completed, generate new scheduled observations on the same area to be completed later.

@@

There are a number of potential Target of Opportunity (ToO) events that Rubin could follow up.
